\textcolor{red}{to be written}
% A preface is written by the author and tells readers how and why the book came into being.
The stream of ideas and experiments in this book started with informal conversations in 2011 with Prof. Jair Koiller over açaí\footnote{A famed brazilian smoothie}, during warm weekend afternoons in Rio de Janeiro, Brazil.

Topics covered included the optics of light rays in an elliptic cavity. Soon this evolved to the closely-related mathematical topic of elliptic billiards, which gave way to budding simulation work (2011) followed by an 8-yr pause.




\textcolor{red}{material below needs to be rewritten}

geometry of elliptic billiard trajectories, following one author's recent work in control of heliostat fields for solar energy plants\footnote{Such fields are in fact a discretized/flattened focusing paraboloid, see \cite{sundrop2016,esolar2017}.}; see \cite{gross2020-solar} for a recent publication. An early, naïve experimental artifact was an animation of 3-periodics in the elliptic billiard along with the locus of their incenter; see  \cite{dsr_vid11incenter}. A natural choice given that each vertex is bisected by the ellipse normal. At the time we did not know this locus could be an ellipse, and indeed, how rare a find this is (we have conjecture that amongst the 5d space of possible ellipse pairs, only in the confocal pair -- a 1d subspace -- can the locus of the incenter be a conic). A twin animation was also produced depicting the self-intersected locus of the intouchpoints; see \cite{dsr_vid11e}.

Shortly thereafter \cite{olga14} produced a proof using methods of complex algebraic geometry.
%by complexification of the phenomenon. 
This was followed by an alternative    proof using techniques of real analytic   geometry given explicitly the equation of the locus; see \cite{garcia2019-incenter}. The loci centroids of Poncelet polygons was studied in \cite{schwartz2016-com}. In  \cite{garcia2019-incenter} the centroid locus was given explicitly.  Also \cite{corentin2021-circum} and \cite{garcia2018} proved that the locus of the circumcenter over billiard 3-periodics is also an ellipse.