\section{Exercises}
\label{sec:07-exercises}

\begin{exercise}
Consider a cubic polynomial $p(z)=(z-\alpha_1)(z-\alpha_2)(z-\alpha_3)$ with simple roots $\alpha_i$ (i=1,2,3).
Let $\beta_1$ and $\beta_2$ the roots of $p'(z)$.
Consider the family of confocal ellipses having foci $\beta_1$ and $\beta_2$.

Show that there exists a unique ellipse $\mathcal E$ in this family passing through the midpoints $(\alpha_i+\alpha_j)/2$, and that it is tangent to the sides of the triangle $T=\{\alpha_1,\alpha_2,\alpha_3\}$. This ellipse is known as Steiner innelipse of $T$.

Conclude that the center of $\E$ is the triangular center  $X_2$ of $T$ and that $T$ is a 3-periodic orbit of a homothetic Poncelet pair.
\end{exercise}

\begin{exercise} Consider an ellipse $\E$ and the set of tangent lines. Show that the set of points of intersection between any two perpendicular
tangents to $\E$  lie on a circle. Find the radius and the center of this circle.
\end{exercise}

\begin{exercise}
Consider a circle $\mathcal{C}$ and a point $P_0$.   Consider the family of circles passing through $P_0$ and internally tangent to $\mathcal{C}$. Show that the set of centers of this family of circles is an ellipse.
Find the semi-axes and the foci of the ellipse.
\end{exercise}

\begin{exercise}
In the proof of \cref{prop:07-X1q2}, let $z_1(\lambda)$, $ z_2(\lambda) $ and $z_3(\lambda)$ the roots of   $E_2(z,\lambda)=0$, $\lambda \in \mathbb{T}$. Show that  the trace of these three curves is an ellipse, i.e., they parametrize the excentral locus.   
\end{exercise}

\begin{exercise}
Consider a triangle inscribed in $\T^1$ with vertices $w_1^2$, $w_2^2$ and $w_3^2$. Show that:
\begin{itemize}
\item The incenter $X_1$ is $-w_1w_2-w_1w_3-w_2w_3$.
\item  The excenters are 
$w_1w_2-w_1w_3-w_2w_3$,\, $-w_1w_2+w_1w_3-w_2w_3$ and $-w_1w_2-w_1w_3+w_2w_3$.
\item The barycenter  $X_2$ is
$(w_1^2+w_2^2+w_3^2)/3$.
\item The orthocenter $X_4$ is
$w_1^2+w_2^2+w_3^2$.
\item The nine-point center $X_5$   is $(w_1^2+w_2^2+w_3^2)/2$.
\end{itemize}
\label{exe:05-X1}
\end{exercise}

\begin{exercise}
Derive the conditions under which a locus of a triangle center becomes degenerate (segment-like) over billiard 3-periodics.
\end{exercise}