%%% BEGIN EXERCISES
\section{Exercises}

\begin{exercise}
Calculate the elliptic billiard aspect ratio $a/b$ such that top and bottom vertices of the elliptic locus of $X_3$ coincide each with the billiard top and bottom vertices. Repeat for the locus of $X_5$.
\end{exercise}

\begin{exercise}
Calculate the elliptic billiard aspect ration $a/b$ such that the locus of $X_4$ is identical to a $90^\circ$ rotated copy of billiard.
\end{exercise}

\begin{exercise}
Over billiard 3-periodics, the envelope of the Euler line is an astroidal-like curve with four cusps, see it \href{https://bit.ly/3yiCvrn}{Live}. Derive its equation. Also, find the elliptic billiard aspect ratio $a/b$ such that the top and bottom cusps of said curve coincide each with top and bottom vertices of the elliptic billiard.
\end{exercise}

\begin{exercise}
Referring to  \cref{fig:04-orthic-incenter}(right), let $T_h$ denote the orthic triangle of an obtuse triangle $T$. Is there another (acute) triangle $T'$ whose orthic is also $T_h$?
\end{exercise}

\begin{exercise}
Express in terms of $a,b$ of the elliptic billiard, the coordinates of the endpoints of the obtuse ``zones'' labeled $P_i^{\perp}$, $i=1,2,3,4$ in  \cref{fig:04-obtuse-zones}.
\end{exercise}

\begin{exercise}
Prove \cref{cor:04-x40-tangent,cor:04-x40-golden}.
\end{exercise}

\begin{exercise}
Let $A$ be area of the four-corner region common to an ellipse and its $90^\circ$-rotated copy and $A_{ell}=\pi a b$ be the area of the ellipse. Show that $A/A_{ell}=4 \csc^{-1}\left[{\sqrt{1 + (a/b)^2}}\right]/\pi$. What is this ara ratio for $a/b=\varphi$?
\end{exercise}

\begin{exercise}
Prove that the motion of $X_{100}$ along the elliptic billiard is opposite to that of the vertices of billiard 3-periodics.
\label{exe:04-x100}
\end{exercise}

\begin{exercise}
Assume $a/b>\alpha_{88}$. Find $t$ in $P_1(t)=[a\cos{t},b\sin{t}]$ where the motion of $X_{88}$ changes direction.
\end{exercise}

\begin{exercise}
Prove that $X_{88}$ coincides with a 3-periodic vertex if and only if $s_2 = (s_1+s_3)/2$. In this case, $X_1$ is the midpoint between $X_{100}$ and $X_{88}$ 
\end{exercise}

\begin{exercise}
Prove \cref{prop:04-x88-env}.
\end{exercise}

\begin{exercise}
Find the unique aspect ratio $a/b>\alpha_4$ of an elliptic billiard which contains right-triangle 3-periodics with sides as 3:4:5. Find aspect ratios for billiards with the next up Pythagorean 3-periodics: 5:12:13, 8:15:17, 7:24:25, 20:21:29. 
\end{exercise}

\begin{exercise}
Let $T$ be a billiard 3-periodic, $T'$ its anticomplementary triangle \cite{mw}, whose sides are parallel to $T$, and $T''$ the latter's intouch triangle. Show that the vertices of $T''$ (the intouchpoints) are always on the elliptic billiard. See it \href{https://bit.ly/3vbk7yu}{Live}. Bonus: prove that the motion of the intouchpoints of $T''$ is non-monotonic assuming $P_1(t)=[a\cos{t},b\sin{t}]$ is monotonic along the billiard. 
\end{exercise}

\begin{exercise}
\label{ex:04-wind}
Referring to \cref{fig:04-inc-wind3}, compute the $\rho$ such that the lobes of $Y(t)$ touch.
% \rho^*=1-(b/a)^2.
\end{exercise}

\section{Research}

\begin{question}
Concerning the locus of $X_{59}$ over billiard 3-periodics (\cref{fig:04-x59-locus}, determine:
\begin{itemize}
\item An implicit and/or parametric equation;
\item The locations of its four self-intersections;
\item The $a/b$ such that if $X_{59}$ is on a self-intersections on the elliptic billiard minor axis, the 3-periodic is a right triangle? (it is close to $1.58$, see \cref{fig:04-x59-locus}(right).
\end{itemize}
\end{question}

\begin{question}
Prove that over billiard 3-periodics traversed continuously, the vertices of the extouch triangle, i.e., the 3 extouchpoints, will move in the same direction as 3-periodic vertices, whereas the Feuerbach point will move in the opposite direction.  
\end{question}

\begin{question}
Derive an expression (implicit and/or parametric) for the locus of $X_{26}$ in either the compact or non-compact case.
\end{question}

\begin{question}
Derive an expression of the non-elliptic locus of the vertices of the anticomplementary triangle over billiard 3-periodics. Show it is always external to the elliptic billiard. Derive its inflection points. See it \href{https://bit.ly/2RtUT00}{Live}.
\end{question}

\begin{question}
\label{que:04-x88-x162}
Derive an expression for $t$ where $X_{88}$ and $X_{162}$ are closest (there are 12 solutions). In \cref{fig:04-3d-torus}, the dashed meridian represents one such minimum which for $a/b=2$ occurs at $t{\simeq}41^\circ$. Notice it does not coincide with any critical points of motion.
\end{question}